Z-Resonance at LEP

### 2010-07-20 Z0-Publikation/tex/paper-template.tex
intro da

\documentclass[epj,nopacs]{svjour}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{latexsym}
\usepackage{amssymb}

@@

\title{Title, z. B. Z-Resonance at LEP}
\titlerunning{Titel, z. B. Z-Resonance at LEP}
\authorrunning{Student1, Student2}
\author{{\bf Draft Version 1.1}\\
\medskip \\
Vorname.~Student1,$^{1}$
Vorname.~Student2$^{1}$
} 
\institute{$^1$Department of Physics, Humboldt University of Berlin, Germany\\}  
\date{Received: \today / Revised version:}
\abstract{
We had a lot of fun measuring the lifetime and the mass of the Z boson! These quantities 
are important to answer the question of life, universe and everything.
Another nice thing we could access was the number of the lepton families, which we 
were especially happy about...  
}
\maketitle

@@

The model describes...
The Z-boson is...
The model parameters are...

It was measured...
.......

>>>>

\documentclass[epj,nopacs]{svjour}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{../../assets/uniinput}

@@

\title{Z-Resonance at LEP}
\titlerunning{Z-Resonance at LEP}
\authorrunning{Thomas Murach, Robert Riemann}
\author{{\bf Draft Version 1.1}\\
\medskip \\
Thomas Murach,$^{1}$
Robert Riemann$^{1}$
} 
\institute{$^1$Department of Physics, Humboldt University of Berlin, Germany\\}  
\date{Received: \today / Revised version:}
\abstract{
We had a lot of fun measuring the lifetime and the mass of the Z boson! These quantities 
are important to answer the question of life, universe and everything.
Another nice thing we could access was the number of the lepton families, which we 
were especially happy about...  
}
\maketitle

@@

The standard model of elementary particles describes interactions of particles
by four fundamental forces. One of them is the electroweak force. It`s gauge
bosons, which mediate the force between the two interacting particles, are the
photon as well as the W$^{\pm}$- and the Z$^0$-boson. At the
electron-positron-collider the Z$^0$ has been seen for the first time, which was
possible because of the sufficient center of mass energy of this collider
experiment.

We were able to evaluate it`s mass $M_Z$ and it`s lifetime τ. The leptonic and
the hadronic decay widths $Γ_l$ and $Γ_h$ could be investigated as well. Finally
the number of quark and lepton families $N_C$ and the weak mixing angle, also
called Weinstein angle, $\Theta_W$ can be measured. This angle describes the
ratio of the electric and the weak coupling constants α and α$_w$.
